\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{csquotes}

\begin{document}

\title{Ethics of User Data: Collection \& Use}

\author{
Oskar Luis Floeck\\
School of Science\\
Royal Melbourne Institute of Technology}

\maketitle

%\tableofcontents

%===========================================================================================

\section{Introduction}

Give an overview of the topic and 
give the reader an idea of what the paper contains and how it is structured. 

It is not intended to replicate the analysis, nor necessarily list out proposed solutions.


1. What is user data? In short why is it collected and briefly state what it can be used for.

In the following report, we will delve into the intricacies behind user data collection and use. Also taking at look at possible legal recourse in Australia, Proposed solutions to various problems faced, and a case study, taking 


As it currently stands, personal user data is not recognised as a fundamental human right. 



%===========================================================================================

\section{Background Analysis}

Use the following framework to perform an analysis and write the results as coherent paragraph structured for a formal report.

\begin{enumerate}
	\item List the known relevant facts
	\item Identify the stakeholders
	\item Discuss the duties and obligations of each of the stakeholders involved
	\item Identify ethical values and social impacts
\end{enumerate}

%===========================================================================================

\section{Legal Recourse Available in Australia}

If someone suffers adversely as a result of the use of technology within your a chosen topic, what legal recourse is
available in Australia? Consider questions such as:
- Who is legally responsible for the negative consequences and why?
- Who
is obligated to ensure no harm can come to those who use this technology, or are involved
in this situation?
- If there
is no specific law to deal with the issue, what could be done?


As it currently stands, Australia is part of the Five-Eyes something something something.



%===========================================================================================

\section{Proposed Solutions}

\paragraph{Make User Data a Fundamental Human Right}

Fundamentally change the view of personal user data to that of a fundamental human right. Allow me to easily and quickly, discover any data that is being collected from me from any service.\\

Services, such as Facebook & Snapchat look to adopt a monthly payment business model. Changing their revenue stream from that of users to people who really want to use the product.

This would reduce income to these services, but have multiple associated benefits. Only users that have deemed the service neccesary to their everyday life would use.

Look at Netflix. They provide a service, movies and series, in which a customerasdasd 

Open-source the data collection used for a service. There are several drawbacks to open-sourcing software, but it is a net benefit. Users can be more sure they are not being exploited. 
However, this can be used for nefarious purposes. Uber did this to Lyft. They analysed Lyft's data between 2014-2016
https://www.theguardian.com/technology/2017/apr/13/uber-allegedly-used-secret-program-to-cripple-rival-lyft



There is no one size fits all solution here. It is going to be entirely dependant upon the corporate entity and their morals to decide the measures they will take to protect and inform users.



%===========================================================================================

\section{Case Study}

Cambridge Analytica & SCL's involvement with influencing the democratic process in the context of the US election among other areas.


 

%===========================================================================================

\section{Conclusion}

The conclusion should give a quick overview of the topics and findings as well as the suggested solutions. It may also contain suggestions for future analysis.

Overview of findings

%===========================================================================================

\section{Bibliography}

References...

%===========================================================================================

\section{Appendix}

A URL to a publicly available OneDrive or Teams shared folder (refer to the References section 4 below) containing your highlighted reference material.

Word count of your essay, excluding the Bibliography and Complimentary sections.

%===========================================================================================

\end{document}

